Blockchain as Middleware Services for\\Transactive Energy Applications

### 2017-04-27 notes/initial_writeup/paper.tex
no message

Microsoft Azure Blockchain as a Service (BaaS) and Project Bletchley~\cite{gray2016introducing}.

Hyperledger Fabric~\cite{hyperledger2017fabric}.

Interledger~\cite{thomas_protocol}.

Bitcoin Lightning Network~\cite{poon2016bitcoin}.

>>>>

Microsoft offers Blockchain as a Service (BaaS) on Azure.
Project Bletchley is Microsoft's architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and cryptlets~\cite{gray2016introducing}.

Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.

Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
a connection between them~\cite{thomas_protocol}.

Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
